\begin{thebibliography}{99}
    %\addcontentsline{toc}{chapter}{参考文献}

    \bibitem{Akasaka00} H. Akasaka, H. Nimiya, K. Soga, S. Matsumoto, K. Emura, N. Miki, E. Emura and K. Takemasa, "Development of expanded amedas weather data for building energy calculation in japan", ASHRAE Transactions, 106:pp.455-465, 2000.

    \bibitem{Agrawal95} R. B. Agrawal and K. Deb, "Simulated binary crossover for continuous search space", Complex systems, Vol. 9, No. 2, pp.115–148, 1995.

    \bibitem{Alhaider15} M. Alhaider and L. Fan, "Mixed Integer Programming for HVACs Operation", In 2015 IEEE Power Energy Society General Meeting, pp.1-5, 2015.

    \bibitem{Autodesk18} Autodesk, "Revit",  \newblock \url{https://www.autodesk.com/products/revit-family/overview/}, 2018.

    \bibitem{BEMA20} 日本ビルエネルギー総合管理技術協会, "建築物エネルギー消費量調査報告【第42報】", 2020.

    \bibitem{Bingham17} R. Bingham, M. Agelin-Chaab and M. A. Rosen, "Multiobjective optimization of a residential building envelope in the Bahamas", In 2017 IEEE International Conference on Smart Energy Grid Engineering (SEGE), pp.294–301, 2017.

    \bibitem{Cheng17} R. Cheng, M. Li, Y. Tian, X. Zhang, S. Yang, Y. Jin and X. Yao, "A Benchmark Test Suite for Evolutionary Many-Objective Optimization", Complex and Intelligent Systems, Vol. 3, pp.67-81, 2017.

    \bibitem{Coello02} C. A. C. Coello, "Theoretical and Numerical Constraint Handling Techniques used with Evolutionary Algorithms: A Survey of the State of the Art", Computer Methods in Applied Mechanics and Engineering, Vol. 191, No.11-12, pp.1245-1287, 2002.

    \bibitem{Deb96} K. Deb and M. Goyal, "A combined genetic adaptive search (GeneAS) for engineering design", Computer Science and informatics, Vol. 26, 30–45, 1996.

    \bibitem{Deb02} K. Deb, A. Pratap, S. Agarwal and T. Meyarivan, "A Fast and Elitist Multiobjective Genetic Algorithm: NSGA-II", IEEE Transactions on Evolutionary Computation, Vol. 6, No. 2, pp.182-197, 2002.

    \bibitem{Deb05} K. Deb, L. Thiele, M. Laumanns and E. Zitzler, "Scalable Test Problems for Evolutionary Multiobjective Optimization", Evolutionary Multiobjective Optimization: Theoretical Advances and Applications, Springer, pp.105-145, 2005.

    \bibitem{Deb14} K. Deb and H. Jain, "An Evolutionary Many-Objective Optimization Algorithm Using Reference-Point-Based Nondominated Sorting Approach, Part I: Solving Problems With Box Constraints", IEEE Transactions on Evolutionary Computation, Vol. 18, No. 4, pp.577-601, 2014.

    \bibitem{EDMC15} 日本エネルギー経済研究所, "EDMCエネルギー・経済統計要覧" ,一般財団法人省エネルギーセンター, 2015.

    \bibitem{EIA17} U. S. Energy Information Administration (EIA), "{\em Annual Energy Outlook 2017}", 2017.

    \bibitem{Enecho17} 経済産業省・資源エネルギー庁, "平成27年度 エネルギーに関する年次報告（エネルギー白書2016）", 2017.

    \bibitem{Esquivel03} S. C. Esquivel and C. A. C. Coello, "On the use of particle swarm optimization with multimodal functions", The 2003 Congress on Evolutionary Computation(CEC2003), Vol. 2, pp.1130-1136, 2003.

    \bibitem{Fudoken19} 日本不動産研究所, "全国オフィスビル調査（2019年1月現在）", 2019.

    \bibitem{Gers00} F. A. Gers, J. Schmidhuber and F. Cummins, "Learning to Forget: Continual Prediction with LSTM", Neural Computation, Vol. 12, No. 10, pp.2451-2471, 2000.

    \bibitem{Gers01} F. A. Gers, "Long Short-Term Memory in Recurrent Neural Networks", Unpublished PhD dissertation, École polytechnique fédérale de Lausanne, Lausanne, Switzerland, 2001.

    \bibitem{Godinez10} A. C. Godinez, L. E. M. Espinosa and E. M. Montes, "An Experimental Comparison of Multiobjective Algorithms: NSGAII and OMOPSO", in 2010 IEEE Electronics, Robotics and Automotive Mechanics Conference, pp.28-33, 2010.

    \bibitem{Goldberg89} D．E．Goldberg, "Genetic Algorithms in Search，Optimization and Machine Learning", Addision-Wesley Reading，1989．

    \bibitem{Haimes71} Y. Y. Hamies, L. S. Lasdon and Wismer, D. A. "On a
    Bicriterion Formulation of the Problems of Integrated System Identification and System Optimization", in IEEE Transactions on Systems, Man. and Cybernetics, SMC-1, No. 3, pp.28-33, 1971.

    \bibitem{Harada07} 原田健，佐久間淳，小野功，小林重信，"関数最適化のための制約対処法：パレート降下修正オペレータ", 人工知能学会論文誌, 22巻, 4号A, pp.364-374, 2007.

    \bibitem{Inouye08} 井上宇市, "空気調和ハンドブック 改訂5版", 丸善出版, 2008

    \bibitem{ISO05} International Organization for Standardization, "ISO 7730:2005 Ergonomics of the thermal environment", 2005

    \bibitem{Iwahashi14} 岩橋 優子, 田辺 新一, 對馬 聖菜, 西原 直枝, 平岡 雅哉, 菰田 英晴, 田渕 誠一, "節電対策が快適性・知的生産性・省エネルギー性に与える影響 東日本大震災後の節電環境下におけるオフィス実態調査に関する研究", 日本建築学会環境系論文集 79 巻 704 号, pp.901-908, 2014.

    \bibitem{JMA19} 気象庁, "天気予報の精度検証結果", \url{https://www.data.jma.go.jp/fcd/yoho/kensho/yohohyoka_top.html}, 2019.

    \bibitem{JMAforecast} 気象庁, "地域時系列予報: 東京地方", \url{https://www.jma.go.jp/en/jikei/319.html}, 2018.

    \bibitem{JMAactual} 気象庁, "過去の気象データ: ダウンロード", \url{http://www.data.jma.go.jp/gmd/risk/obsdl/index.php}, 2018.

    \bibitem{Kamimura08} 神村 一幸, 杵嶋 修三, 平 卯太郎, 藤沼 康実, 吉田 友紀子, 内海 康雄,"BEMS（ビルエネルギーマネージメントシステム）導入における省エネの可能性", 家庭・業務部門の温暖化対策, pp.143–152, 2008.

    \bibitem{Kanto11} 関東経済産業局, "中小企業の支援担当者向け 省エネ導入ガイドブック" , 2011.

    \bibitem{Kennedy95} J. Kennedy and R. Eberhart, "Particle swarm optimization", in Proceedings of ICNN'95 - International Conference on Neural Networks, Vol.4, pp.1942-1948, 1995.

    \bibitem{Kita99} 喜多 一, 小野 功, 小林 重信, "実数値GAのための正規分布交叉に関する理論的考察", 計測自動制御学会論文集, Vol.35, No.11, pp.1333-1339, 1999

    \bibitem{Knowles10} Knowles,~J.~D., Watson,~R.~A., and Corne,~D.~W., "Reducing Local Optima in Single-Objective Problems by Multi-objectivization", {\em Evolutionary Multi-Criterion Optimization}, pp.269-283, 2001.

    \bibitem{Kuki12} 空気調和・衛生工学会(編), "試して学ぶ熱負荷HASPEE～新最大熱負荷計算法～" ,丸善, 2006.

    \bibitem{Kuki16} 空気調和・衛生工学会 空調設備委員会 新設計条件適応空調システム検討小委員会, "新設計条件適応空調システム調査報告書", 空気調和・衛生工学会レポート, R 1037-2016, 2016.

    \bibitem{Li09} H. Li and Q. Zhang, "Multiobjective Optimization Problems With Complicated Pareto Sets, MOEA/D and NSGA-II", IEEE Transactions on Evolutionary Computation, Vol. 13, No. 2, pp.284-302, 2009.

    \bibitem{Nakayama08} 中山弘隆, 岡部達哉, 荒川雅生, 尹禮分, "多目的最適化と工学設計-しなやかシステム工学設計アプローチ-", 現代図書, 2008.

    \bibitem{Nebro15} A. J. Nebro, J. J. Durillo and M. Vergne, "Redesigning the jMetal Multi-Objective Optimization Framework", in Proceedings of the Companion Publication of the 2015 Annual Conference on Genetic and Evolutionary Computation, GECCO Companion ’15, pp.1093–1100, 2015.

    \bibitem{NREL19} National Renewable Energy Laboratory, "EnergyPlus", \newblock \url{https://energyplus.net/}, 2019.

    \bibitem{NTA19} 国税庁企画課, "平成30年分民間給与実態統計調査結果について", \url{https://www.nta.go.jp/information/release/kokuzeicho/2019/minkan/index.htm}, 2019.

    \bibitem{Ohta13} 太田 恵大, 浮穴 朋興, 稲田 徹, "多目的最適化手法によるビル設備制御", 計測自動制御学会システム・情報部門学術講演会2013(SSI2013)講演論文集, pp.349-354, 2013.

    \bibitem{Ono97} I. Ono and S. Kobayashi, "A Real-coded Genetic Algorithm for Function Optimization Using Unimodal Normal Distribution Crossover", in Proc. of 7th ICGA, pp.246-253, 1997.

    \bibitem{Pan16} L. Pan, K. Li, W. Xue, and G. Liu, "Multi-objective optimization for building performance design considering thermal comfort and energy consumption", In 2016 35th Chinese Control Conference (CCC). pp.2799–2803, 2016.

    \bibitem{Price06} K. Price, R. M. Storn and J. A. Lampinen, "Differential
    evolution: a practical approach to global optimization", Springer Science \& Business Media, 2006.

    \bibitem{Ray01} T. Ray, K. Tai and K. C. Seow, "Multiobjective Design Optimization by an Evolutionary Algorithm", Engineering Optimization, Vol. 33, No. 4, pp. 399-424, 2001.

    \bibitem{Shigen16} 経済産業省資源エネルギー庁, "ZEBロードマップ検討委員会におけるZEBの定義・今後の施策など", \url{https://www.enecho.meti.go.jp/category/saving_and_new/saving/zeb_report/pdf/report_160212_ja.pdf}, 2016.

    \bibitem{Sierra05} M. R. Sierra and C. A. C. Coello, "Improving PSO-Based Multi-objective Optimization Using Crowding, Mutation and $\epsilon$-Dominance", In Evolutionary Multi-Criterion Optimization. pp.505-519, 2005.

    \bibitem{Sutskever14} I. Sutskever, O. Vinyals and Q. Le, "Sequence to sequence learning with neural networks", Advances in NIPS, 2014.

    \bibitem{Takagi11} 高木 康夫, 村山 大, 花田 雄一, 森本 博之, 野田 周平, 蔦宗 俊一, 志村 貴司, 香月 康彦, "快適性と省エネルギーを両立させるオフィス空調システムの開発", 空気調和・衛生工学会大会学術講演論文集, pp.1579-1582, 2011.

    \bibitem{Tanabe20} R. Tanabe and H. Ishibuchi, "A Review of Evolutionary Multimodal Multiobjective Optimization",  in IEEE Transactions on Evolutionary Computation, Vol. 24, No. 1, pp.193-200, 2020.

    \bibitem{Tresidder12} E. Tresidder, Y. Zhang and A. I. Forrester, "Acceleration of Building Design Optimisation Through the Use of Kriging Surrogate Models", in Proceedings of Building Simulation and Optimization(BSO12), pp.1-8, 2012.

    \bibitem{Ueda10} 上田 悠, 太宰 龍太, 綛田 長生, 伊香賀 俊治, 加藤 彰浩, "学習/多目的最適化機能を組み込んだ空調制御技術の実験的研究", 計測自動制御学会論文集, Vol. 46, No. 8, pp.439–337, 2010.

    \bibitem{Weather17} 株式会社ウェザーニューズ, "1kmメッシュ＆5分更新の超細密天気予報をアプリ「ウェザーニュースタッチ」で配信開始", \url{https://jp.weathernews.com/news/17284/}, 2017.

    \bibitem{WGBC14} World Green Building Council, "Health, Wellbeing and Productivity in Offices: The Next Chapter for Green Building", \url{http://www.worldgbc.org/news-media/health-wellbeing-and-productivity-offices-next-chapter-green-building}, 2014.

    \bibitem{Xiao17} J. Xiao, J. Xie, X. Chen, K. Yu, Z. Chen, and Z. Li, "Energy Cost Reduction Robust Optimization for Meeting Scheduling in Smart Commercial Buildings", In 2017 IEEE Conference on Energy Internet and Energy System Integration (EI2). pp.1-5, 2017.

    \bibitem{Xu13} Y. Xu, K. Ji, Y. Lu, Y. Yu, and W. Liu, "Optimal Building Energy Management using Intelligent Optimization", In 2013 IEEE International Conference on Automation Science and Engineering (CASE). pp.95-99, 2013.

    \bibitem{Xymax19} ザイマックス不動産総合研究所, "1人あたりオフィス面積調査（2019年）", \url{https://soken.xymax.co.jp/2019/10/02/1910-office_space_per_person_2019/}, 2019.

    \bibitem{ZEB18} ZEBロードマップ フォローアップ委員会, "ZEB設計ガイドライン ZEB Ready・中規模事務所編 Ver.1", \url{https://sii.or.jp/zeb/guideline/comment/download/file15/FA2NMWku7e}, 2018.

    \bibitem{Zhang07} Q. Zhang and H. Li, "MOEA/D: A Multiobjective Evolutionary Algorithm Based on Decomposition", IEEE Transactions on Evolutionary Computation, Vol. 11, No. 6, pp.712-731, 2007.

    \bibitem{Zhang08} Q. Zhang, A. Zhou, S. Zhao, P. N. Suganthan, W. Liu and S. Tiwari, "Multiobjective optimization Test Instances for the CEC 2009 Special Session and Competition", Technical Report, CES-487, University of Essex and Nanyang Technological University, 2008.

    \bibitem{Zhang14} Y. Zhang, P. Zeng and C. Zang, "Multi-objective optimal control algorithm for HVAC based on particle swarm optimization", in Fifth International Conference on Intelligent Control and Information Processing, pp.417-423, 2014.

    \bibitem{Zitzler99} E. Zitzler and L. Thiele, "Multiobjective evolutionary algorithms: a comparative case study and the strength Pareto approach", in IEEE Transactions on Evolutionary Computation, Vol.3, No.4, pp.257-271, 1999.

\end{thebibliography}
